Case Study (McKenna)

### 2020-09-25 Cases/mrp/Case Study (McKenna) .Rmd
Working on the postratifying code.

[Note to McKenna]
Questions to answer: 
Why cauchy?
Actual model specification?
Why varying coefficients?

@@

  int<lower=0,upper=n_age> age[n];                    // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                    // the observed data for each
  int<lower=0,upper=n_income> income[n];              // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                  // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                          // Model parameters to be estimated:
  real b0;                                            // "intercept"
  real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
  real a_income[n_income];                            // income varying coeffs (depart linear fit)
  real a_male[n_male];                                // gender varying coeffs
  real a_state[n_state];                              // state varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
  real<lower=0> sigma_income;                         // income var(sd) component
  real<lower=0> sigma_male;                           // gender fluency var(sd) component
  real<lower=0> sigma_state;                          // state var(sd) component
}
transformed parameters {                              // Model specification is here
  vector[n] outcome_hat;
  for (i in 1:n) {
    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
  }
}
model {                                              // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodelled                                                                // Can modify Cauchy scale parameter
                                                     // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                      // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
                                                     // normal distribution with an additional
                                                     // variance component, i.e.
                                                     // outcome ~ normal(outcome_hat, sigma_outcome)
                                                     // Note the prior distributions for 
                                                     // unmodelled parameters will change.
}
```

>>>>

[Note to McKenna]
Questions to answer: 
Why cauchy?
Actual model specification? - looks like the model is specified in the transformed parameters section. why?
Why varying coefficients?

@@

  int<lower=0,upper=n_age> age[n];                    // These are the variables containing
  int<lower=0,upper=n_eth> eth[n];                    // the observed data for each
  int<lower=0,upper=n_income> income[n];              // poststratification factor in the 
  int<lower=0,upper=n_male> male[n];                  // final model
  int<lower=0,upper=n_state> state[n];      
 }
parameters {                                          // Model parameters to be estimated:
  real b0;                                            // "intercept"
  real a_age[n_age];                                  // age varying coeffs (depart from linear fit)
  real a_eth[n_eth];                                  // ethnicity class varying coeffs 
  real a_income[n_income];                            // income varying coeffs (depart linear fit)
  real a_male[n_male];                                // gender varying coeffs
  real a_state[n_state];                              // state varying coeffs
  real<lower=0> sigma_age;                            // age var(sd) component
  real<lower=0> sigma_eth;                            // ethnicit var(sd) component
  real<lower=0> sigma_income;                         // income var(sd) component
  real<lower=0> sigma_male;                           // gender fluency var(sd) component
  real<lower=0> sigma_state;                          // state var(sd) component
}
// transformed parameters {                              // Model specification is here
//   vector[n] outcome_hat;
//   for (i in 1:n) {
//    outcome_hat[i] = b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]];
//   }
// }
model {                                              // Model distributions for varying coefficients
  b0 ~ cauchy(0,2.5);                                // and prior distributions for unmodelled                                                                // Can modify Cauchy scale parameter
                                                     // Can also specify a uniform distribution here
  a_age ~ normal(0, sigma_age);                      // or by setting upper and lower limits for
  a_eth ~ normal(0, sigma_eth);                      // unmodelled parameters in the parameter step
  a_income ~ normal(0, sigma_income);                // above  
  a_male ~ normal(0, sigma_male);                      
  a_state ~ normal(0, sigma_state);

@@

  for (i in 1:n) {
   outcome[i] = bernoulli_logit(b0 + a_age[age[i]] + a_eth[eth[i]] + a_income[income[i]] + a_male[male[i]] + a_state[state[i]]);
  }

//  outcome ~ bernoulli_logit(outcome_hat);            // For a continuous outcome, specify a
                                                     // normal distribution with an additional
                                                     // variance component, i.e.
                                                     // outcome ~ normal(outcome_hat, sigma_outcome)
                                                     // Note the prior distributions for 
                                                     // unmodelled parameters will change.
}
```
